Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-16 review_article.Rmd
added package reference

## Limitations of different choices

Cartograms provide the spatial distortion to more accurately convey the statistical distribution, focuses on the human impact of the disease. However, the transformation of contiguous cartograms often occurs at the expense of the shape of areas [@CBATCC, @NAC, @TAAM]. When the population density pf the geographic units is highly dissonant with geographic density, the cartogram will lose all spatial context.
Dorling [@ACTUC] has a cartogram showing the 1966 general election results, which looked very little like the geographical shape of Australia.

@@

The following R [@R] packages were used to produce this paper: tidyverse [@tidyverse], RColorBrewer [@RColorBrewer], ggthemes [@ggthemes], png [@png], cowplot [@cowplot], sf [@sf], spData [@spData], cartogram [@cartogram], sugarbag [@sugarbag], knitr [@knitr], rmarkdown [@rmarkdown].

>>>>

## Limitations of alternative displays

Cartograms provide the spatial distortion to more accurately convey the statistical distribution, focuses on the human impact of the disease. However, the transformation of contiguous cartograms often occurs at the expense of the shape of areas [@CBATCC, @NAC, @TAAM]. When the population density of the geographic units is highly dissonant with geographic density, the cartogram will lose all spatial context.
Dorling [@ACTUC] has a cartogram showing the 1966 general election results, which looked very little like the geographical shape of Australia.

@@

The following R [@R] packages were used to produce this paper: tidyverse [@tidyverse], RColorBrewer [@RColorBrewer], ggthemes [@ggthemes], png [@png], cowplot [@cowplot], sf [@sf], spData [@spData], cartogram [@cartogram], sugarbag [@sugarbag], knitr [@knitr], rmarkdown [@rmarkdown] and absmapsdata [@ABSmaps].
